\documentclass[11pt,oneside,letterpaper]{amsart}
\usepackage[color, boxed]{/Users/aden/Library/CloudStorage/Box-Box/latex/adenc}

\title{\texttt{adenc.sty}}
\author{Aden Chen}

\usepackage{float}
\renewcommand{\arraystretch}{1.5}
\usepackage[table]{xcolor}

\renewcommand{\familydefault}{\sfdefault}
\usepackage{courier}

\begin{document}
\maketitle
\tableofcontents

New to \LaTeX?
Want to create beautiful documents?
Check out the \href{https://github.com/AdenChen27/latex}{\texttt{adenc}} package!

\section{Package Options}
The following package options are supported:
\begin{itemize}
  \item \verb|color| adds background colors for theorem environments (see \Cref{sec:thm-env}). 
  \item \verb|plain| uses the default theorem environments (\texttt{definition}, \texttt{plain}, and \texttt{remark}); \verb|boxed| adds a box around the theorem environments.
  You may choose between one of the two (default is \verb|plain|).
  \item \verb|hideproofs| and \verb|hidemarkings| hide, respectively, proof environments and markings generated using the \verb|\markabove| and \verb|\markbelow| commands (see \Cref{sec:marking}). 
  \item \verb|workingpaper| adds (1) a watermark with date on the first page to indicate that the current document is a draft and (2) more space to the margin so that notes written with the \verb|\todo| command (using the \verb|todonotes| package) can fully display. 
\end{itemize}

\noindent
To pass an option, use: \verb|\usepackage[Option]{adenc}|

\noindent
To pass multiple options, use: \verb|\usepackage[Option1, Option2, ...]{adenc}|


\section{Theorem Environments}
\label{sec:thm-env}

\begin{definition}
  A definitive \vocab{definition} is a definition, by definition. 
\end{definition}
\begin{lemma}
  A lamentable lemma. 
\end{lemma}
\begin{theorem}
  A towering theorem. 
\end{theorem}
\begin{corollary}
  A cool corollary. 
\end{corollary}
\begin{remark}
  A remarkable remark. 
\end{remark}
\begin{example}
  An exemplary example. 
\end{example}
\begin{problem}
  A problematic problem. 
\end{problem}
\begin{proof}
  A precise proof.
\end{proof}

Numbering can be turned off by using the corresponding \verb|*| versions of the environments (e.g. \verb|theorem*| instead of \verb|theorem|). 


\section{Marking the Document}
\label{sec:marking}
The \verb|\todo| command in the \verb|todonotes| package is a great way to add notes to a document, but among other things, it does not support display style math and, when used frequently, the places to which they point can\todo{E.g., this points to the word ``can.'' } be hard\todo{And this to ``hard.'' } to decipher. 
It is for these reasons that the following commands are introduced:
\begin{enumerate}[label=(\alph*)]
  \item \verb|\begin{itodo} ... \end{itodo}| (\underline{i}nline \underline{todo}) produces an inline block of notes. 
    This can be used as placeholders for contents to be added later. 
    \begin{itodo}
      This is an example of what notes produced by the \texttt{itodo} environment looks like. 
        Unlike the \texttt{\textbackslash todo} command, the \texttt{itodo} environment supports display math:
      \[
        \sum_{n=1}^{\infty} a_n z^n . 
      \] 
    \end{itodo}
  \item \verb|\markabove| and \verb|\markbelow| provide a way to mark texts without altering the spacing. 
  Both commands take two arguments: (1) align method (\verb|l|, \verb|c|, or \verb|r|); and (2) text to display. 
  For example, 

  \begin{mdframed}
    \noindent
    Test test test\markabove{l}{test1} test\markbelow{c}{I'm marking below here}.

    \noindent
    Test test test test.

    \noindent
    Test test test\markabove{c}{above!} test\markbelow{r}{math! \(\alpha\)}.
  \end{mdframed}
  is produced by the following code:
\end{enumerate}
\begin{verbatim}
Test test test\markabove{l}{test1} test\markbelow{c}{I'm marking below here}.

Test test test test.

Test test test\markabove{c}{above!} test\markbelow{r}{math! \(\alpha\)}.
\end{verbatim}


\section{New Commands}
Some commands (mainly for math symbols) are added or modified for aesthetics and/or convenience.
A few notable ones are mentioned below:

\begin{table}[H]
\centering
\begin{tabular}{ p{.5\linewidth} l l } 
  \textbf{Description}  & \textbf{Example} & \textbf{LaTeX Commands} \\ 
  \hline
  Command for styling new vocabulary\footnotemark
    & \vocab{vocab}
    & \verb|\vocab{vocab}| \\ 
  Contradiction symbol
    & \contradiction
    & \verb|\contradiction| \\ 
  Shortcuts for \verb|\mathbb|
    & \(\RR, \QQ, \FF, \PP\)
    & \verb|\RR, \QQ, \FF, \PP| \\
  Shortcuts for \verb|\mathcal|
    & \(\cA, \cB, \cC, \cD\)
    & \verb|\cA, \cB, \cC, \cD| \\
  Shortcuts for \verb|\mathsf|
    & \(\sL, \sT, \sU, \sV\)
    & \verb|\sL, \sT, \sU, \sV| \\
  Better looking complement symbol
    & \(A^\complement\)
    & \verb|A^\complement| \\ 
  Better looking empty set symbol
    & \(\emptyset\)
    & \verb|\emptyset| \\ 
  Command for vectors
    & \(\vec{v}\)
    & \verb|\vec{v}| \\ 
  Shortcuts for matrices
    & \(\bmat{1 & 2 \\ 3 & 4}\)
    & \verb|\bmat{1 & 2 \\ 3 & 4}| \\ 
    & \(\pmat{1 & 2 \\ 3 & 4}\)
    & \verb|\pmat{1 & 2 \\ 3 & 4}| \\ 
    &\(\vmat{1 & 2 \\ 3 & 4}\)
    & \verb|\vmat{1 & 2 \\ 3 & 4}| \\ 
  Differentiation operators
    & \(\d x, \D f\)
    & \verb|\d x, \D f|\\
  (Use \verb|\dd| in integrals for correct spacing.)
    & \(\ds \int f \dd x\)
    & \verb|\int f \dd x| \\ 
  Imaginary number
    & \(\I\) 
    & \verb|\I| \\ 
  The indicator function
    & \(\ind\)
    & \verb|\ind| \\
  Independent
    & \(\indep\)
    & \verb|\indep|
\end{tabular}
\end{table}
\footnotetext{In, for example, definitions.}


\section{Credits}
I have stolen a lot of stuff from below:
\begin{itemize}
  % \item \href{https://web.stanford.edu/~lindrew/}{Andrew Lin}'s package, \href{https://web.stanford.edu/~lindrew/lindrew.sty}{lindrew}.
  \item \url{https://web.stanford.edu/~lindrew/lindrew.sty} 
  % \item \href{https://github.com/gillescastel}{Gilles Castel}'s \href{https://github.com/gillescastel/lecture-notes/blob/master/algebraic-topology/preamble.tex}{preamble file} for his \href{https://github.com/gillescastel/lecture-notes}{lecture notes}. 
  \item \url{https://github.com/gillescastel/lecture-notes} 
  \item \url{https://tex.stackexchange.com/questions/142242/robust-way-to-mark-draft-text} 
  \item \url{https://math.stackexchange.com/questions/160039/are-there-any-symbols-for-contradictions} 
\end{itemize}

\end{document}
